Elaboration with First-Class Implicit Function Types

### 2020-03-03 paper.tex
fix

\begin{figure}
\begin{alignat*}{4}
  & IdTy   && :\equiv \{A : \U\}\to A \to A   \hspace{10em}         && inc    && : Int \to Int                                        \\
  & single && : \{A : \U\} \to A \to List\,A                       && auto   && : IdTy \to IdTy                                      \\
  & id     && : IdTy                                               && auto'  && : \{B : \U\}\to IdTy \to B \to B                     \\
  & ids    && : List\,IdTy                                         && choose && : \{A : \U\} \to A \to A \to A                       \\
  & nil    && : \{A : \U\}\to List\,A                              && app    && : \{A\,B : \U\} \to (A \to B) \to A \to B            \\
  & cons   && : \{A : \U\} \to A \to List\,A \to List\,A           && revapp && : \{A\,B : \U\} \to A \to (A \to B) \to B            \\
  & head   && : \{A : \U\} List\,A \to A                           && runST  && : \{A : \U\} \to (\{S : \U\} \to ST\,S\,A) \to A     \\
  & tail   && : \{A : \U\} List\,A \to List\,A                     && argST  && : \{S : \U\}\to ST\,S\,Int                           \\
  & map    && : \{A B : \U\} \to (A \to B) \to List\,A \to List\,B && poly   && : IdTy \to Pair\,Int\,Bool
\end{alignat*}
\caption{Types used in Figure \ref{fig:benchmark}.}
\label{fig:benchmark_types}
\end{figure}

>>>>

\begin{figure}
\begin{alignat*}{4}
  & IdTy   && :\equiv \{A : \U\}\to A \to A   \hspace{10em}         && inc    && : Int \to Int                                        \\
  & single && : \{A : \U\} \to A \to List\,A                       && auto   && : IdTy \to IdTy                                      \\
  & id     && : IdTy                                               && auto'  && : \{B : \U\}\to IdTy \to B \to B                     \\
  & ids    && : List\,IdTy                                         && choose && : \{A : \U\} \to A \to A \to A                       \\
  & nil    && : \{A : \U\}\to List\,A                              && app    && : \{A\,B : \U\} \to (A \to B) \to A \to B            \\
  & cons   && : \{A : \U\} \to A \to List\,A \to List\,A           && revapp && : \{A\,B : \U\} \to A \to (A \to B) \to B            \\
  & head   && : \{A : \U\} \to List\,A \to A                           && runST  && : \{A : \U\} \to (\{S : \U\} \to ST\,S\,A) \to A     \\
  & tail   && : \{A : \U\} \to List\,A \to List\,A                     && argST  && : \{S : \U\}\to ST\,S\,Int                           \\
  & map    && : \{A B : \U\} \to (A \to B) \to List\,A \to List\,B && poly   && : IdTy \to Pair\,Int\,Bool
\end{alignat*}
\caption{Types used in Figure \ref{fig:benchmark}.}
\label{fig:benchmark_types}
\end{figure}
